Visualizations for the manuscript

### 2022-03-29 metanalysis_visualization/manuscript_Figures.Rmd
beginning working on ITS

bootstrapping_slopes <- function(patient_count_psy_period_psy, 
                                    bootstrap_size) {
  bootstrapped_timepoints <- mapply(binom_proportion,
                                    n = bootstrap_size,
                                    size = patient_count_psy_period_psy$count_no_psy_patients +
                                      patient_count_psy_period_psy$count_psy_patients,
                                    prob = patient_count_psy_period_psy$percentage/100)
  bootstrapped_sample_list <- vector(mode = "list", length = bootstrap_size)
  bootstrapped_coefficients_list <- vector(mode = "list", length = bootstrap_size)
  for (iteration in 1:bootstrap_size) {
    df_iteration <- data.frame(period = patient_count_psy_period_psy$period,
                               time = patient_count_psy_period_psy$time,
                               percentage = bootstrapped_timepoints[iteration, ])
    ts_linear_percent <- lm(percentage ~ period * time, df_iteration)
    linear_model <- broom::tidy(ts_linear_percent) %>%
      filter(term %in% c("time", "periodduring_pandemic:time"))
    coefficients <- linear_model$estimate
    names(coefficients) <- linear_model$term
    bootstrapped_coefficients_list[[iteration]] <- coefficients
    df_iteration$predicted <- predict(ts_linear_percent)
    df_iteration$time_p <- patient_count_psy_period_psy$time_p
    bootstrapped_sample_list[[iteration]] <- df_iteration
  }
  bootstrapped_fitted_df <- bind_rows(bootstrapped_sample_list, .id = "iteration")
  bootstrapped_coefficients_df <- bind_rows(bootstrapped_coefficients_list,
                                          .id = "iteration")
  return(list(bootstrapped_coefficients_df, 
              bootstrapped_fitted_df))
}

# Get count_icd_all in the same format that patient_count_psy_period_psy_all, because first n last months missing ... 
count_icd_all_boot <- count_icd_all %>% 
  group_by(siteid) %>% # necessary to generate time correctly 
  rename(count_psy_patients = count_psy, 
         percentage = percentage_psy) %>% 
  mutate(count_no_psy_patients = count_icd - count_psy_patients, 
         month_year = format(time_p, "%m"),
         time = seq_along(time_p))

>>>>

bootstrapping_slopes <- function(patient_count_psy_period_psy, 
                                    bootstrap_size) {
  bootstrapped_timepoints <- mapply(binom_proportion,
                                    n = bootstrap_size,
                                    size = patient_count_psy_period_psy$count_no_psy_patients +
                                      patient_count_psy_period_psy$count_psy_patients,
                                    prob = patient_count_psy_period_psy$percentage/100)
  bootstrapped_sample_list <- vector(mode = "list", length = bootstrap_size)
  bootstrapped_coefficients_list <- vector(mode = "list", length = bootstrap_size)
  for (iteration in 1:bootstrap_size) {
    df_iteration <- data.frame(period = patient_count_psy_period_psy$period,
                               time = patient_count_psy_period_psy$time,
                               percentage = bootstrapped_timepoints[iteration, ])
    ts_linear_percent <- lm(percentage ~ period * time, df_iteration)
    linear_model <- broom::tidy(ts_linear_percent) %>%
      filter(term %in% c("time", "periodduring_pandemic:time"))
    coefficients <- linear_model$estimate
    names(coefficients) <- linear_model$term
    bootstrapped_coefficients_list[[iteration]] <- coefficients
    df_iteration$predicted <- predict(ts_linear_percent)
    df_iteration$time_p <- patient_count_psy_period_psy$time_p
    bootstrapped_sample_list[[iteration]] <- df_iteration
  }
  bootstrapped_fitted_df <- bind_rows(bootstrapped_sample_list, .id = "iteration")
  bootstrapped_coefficients_df <- bind_rows(bootstrapped_coefficients_list,
                                          .id = "iteration")
  return(list(bootstrapped_coefficients_df, 
              bootstrapped_fitted_df))
}
```

```{r}
# Get count_icd_all in the same format that patient_count_psy_period_psy_all, because first n last months missing ... 
count_icd_all_boot <- count_icd_all %>% 
  group_by(siteid) %>% # necessary to generate time correctly 
  rename(count_psy_patients = count_psy, 
         percentage = percentage_psy) %>% 
  mutate(count_no_psy_patients = count_icd - count_psy_patients, 
         month_year = format(time_p, "%m"),
         time = seq_along(time_p))
